Untitled

### 2023-09-25 code/analysis_Redo.Rmd
Exploring alternatives

dfc %>% 
  filter(Year == 2010) %>% 
  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
  select(Treat, Total, Pct.NHA:Pct.COM) %>% 
  #filter(!complete.cases(.)) %>% 
  tbl_summary(by = Treat, 
                statistic = list(all_continuous() ~ "{mean} ({sd})")) %>% 
  add_p()

@@

```{r}
## Plot
p <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>%
  group_by(`BHCMIS ID`, Year) %>%
  summarise(Clinics = max(Clinics, na.rm = TRUE)) %>%
  group_by(Year, Clinics) %>% 
  summarise(Count = n()) %>% 
  mutate(CompetitorsInArea = factor(ifelse( Clinics < 4, Clinics - 1, "3+"))) %>% 
  group_by(Year, CompetitorsInArea) %>% 
  summarise(Count = sum(Count))

@@

for (i in 12:19){
  df.temp <- df.spill3[,c(1:5, 11, i, 16:ncol(df.spill3))]
  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[3,])
}

@@

>>>>

dfc %>% 
  filter(Year == 2010) %>% 
  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
  select(Treat, Total, Pct.NHA:Pct.COM) %>% 
  #filter(!complete.cases(.)) %>% 
  tbl_summary(by = Treat, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"),
missing = "no") %>% 
  add_p()

@@

```{r}
## Plot
p <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>%
  group_by(`BHCMIS ID`, Year) %>%
  summarise(Clinics = max(Clinics, na.rm = TRUE)) %>%
  group_by(Year, Clinics) %>% 
  summarise(Count = n()) %>% 
  mutate(CompetitorsInArea = factor(ifelse( Clinics < 4, Clinics - 1, "3+"))) %>% 
  group_by(Year, CompetitorsInArea) %>% 
  summarise(Count = sum(Count)) %>% 
  filter(CompetitorsInArea != "-Inf")

@@

for (i in 12:19){
  df.temp <- df.spill3[,c(1:5, 11, i, 16:ncol(df.spill3))]
  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Sites | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[3,])
}

@@

did2s(
      data = df.spill3 %>% mutate(clust = substr(Zip, 1, 3)), 
      yname = "Sites", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)) ,
        cluster_var = "clust",
      verbose = FALSE
    )
